\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-05 theory.tex
Updated labels on Fig 1

 \begin{table}[htb]
\label{tab:Tl_nu}
\begin{center}
\begin{tabular}{ | l | c | c  | c |}
\hline
Case & $T_\ell$ & $\nu$ & Used in \\ \hline
\citet{kitching/etal:2016} `Standard' & $1$ & $\ell$ & pre-2014 CFHTLenS papers \\
Baseline Limber Flat Sky &  $\ell^4 / (\ell + 0.5)^4$ & $\ell$ & \\
Baseline Limber Spherical & equation~\ref{eqn:Tl} & $\ell$ & \\
Extended Limber Flat Sky & $\ell^4 / (\ell + 0.5)^4$ & $\ell + 0.5$ & \\
Extended Limber Spherical & equation~\ref{eqn:Tl}& $\ell + 0.5$  & \\
Extended `Standard' & $1$ & $\ell + 0.5$ & \citet{joudaki/etal:2016} \&  \\
  & & & \citet{hildebrandt/etal:2016}$^*$\\\hline
 \end{tabular}
 \end{center}
 \caption{Variations on the different approximations that can be made when calculating the convergence power spectrum $P_\kappa(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.  $^*$We confirm that there is a typographical error in equation 4 of \citet{hildebrandt/etal:2016} which does not include the extra term of `$+0.5$' in $\nu$ that was incorporated in the cosmological analysis.}  
 \end{table}

@@

 \begin{figure}
 \begin{center}
 \includegraphics[width=0.5\textwidth]{figures/Cl_xi_comp.pdf}
 \label{fig:Cl_xi}
 \caption{\emph{Top:} Theoretical models of the $\kappa$ power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right})for the different approximations discussed in \citet{kitching/etal:2016}. \emph{Bottom:} Deviations with respect to the full treatment (LSH).\red{ Fig 3 in Kitching et al. is showing $C_\ell$ not $\ell(\ell+1)/2\pi C_\ell$. Would be better to show the same thing here ($C_\ell$ instead of $\ell C_\ell$ with the same axes range).} }
 \end{center}
 \end{figure}

>>>>

 \begin{table}[htb]
\label{tab:Tl_nu}
\begin{center}
\begin{tabular}{ | l | l | c | c  | c |}
\hline
Case & ID & $T_\ell$ & $\nu$ & Used in \\ \hline
\citet{kitching/etal:2016} `Standard' & KSt & $1$ & $\ell$ & pre-2014 CFHTLenS papers \\
Baseline Limber `Flat' Sky &  LF & $\ell^4 / (\ell + 0.5)^4$ & $\ell$ & \\
Baseline Limber Spherical & LS & equation~\ref{eqn:Tl} & $\ell$ & \\
Extended Limber `Flat' Sky & ELF & $\ell^4 / (\ell + 0.5)^4$ & $\ell + 0.5$ & \\
Extended Limber Spherical & ELS & equation~\ref{eqn:Tl}& $\ell + 0.5$  & \\
Extended Standard Flat Sky & ESt & $1$ & $\ell + 0.5$ & \citet{joudaki/etal:2016} \&  \\
  &  & & & \citet{hildebrandt/etal:2016}$^*$\\\hline
 \end{tabular}
 \end{center}
 \caption{Variations on the different approximations that can be made when calculating the shear power spectrum $P_\gamma(\ell)$ (equation~\ref{eqn:Pkappa}), using a Limber approximation.  $^*$We apologise for the typographical error in equation 4 of \citet{hildebrandt/etal:2016} which should include the extra term of `$+0.5$' in $\nu$ that was incorporated in the cosmological analysis.} 
 \end{table}

@@

 \begin{figure}
 \begin{center}
 \includegraphics[width=0.75\textwidth]{figures/Cl_xi_comp.pdf}
 \label{fig:Cl_xi}
 \caption{\emph{Upper Panels:} Theoretical models for the shear power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right}) for the different approximations listed in Table~\ref{tab:Tl_nu}. \emph{Lower Panels:} Deviations with respect to the full treatment (ELS).}
 \end{center}
 \end{figure}
